Output Summary

### 2021-12-09 03-post-process/output-plots.Rmd
Include new parameters in MCMC diagnostics

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Parr Recruitment"
L2 = c("BH Productivity", "BH Capacity", "Process SD", "Among-pop Correlation", "Parr States")
match = c("alpha", "^beta[", "sig_lPb", "rho_lPb", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

>>>>

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Parr Recruitment"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Parr States")
match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_lPb", "rho_lPb", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
